%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\newcommand{\delim}{\hspace{.1em}\textbullet\hspace{.25em}}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Benjamin D. Killeen}
  & \href{mailto:killeen@jhu.edu}{killeen@jhu.edu}\\
  \href{https://benjamindkilleen.com}{benjamindkilleen.com}
  & \href{tel:3146516809}{(314) 651-6809} \\
\end{tabular*}


% -----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{The Johns Hopkins University}{Baltimore, MD}
{Ph.D. in Computer Science}{Expected: 2024\vspace{.2cm}}
\resumeSubheading
{University of Chicago}{Chicago, IL}
{Bachelors in Computer Science with Honors}{June 2019\vspace{.2cm}}
\textit{\small Minor in Physics \hfill GPA: 3.81}
\resumeSubHeadingListEnd


% -----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{University of Chicago}{Chicago, IL}
{Instructional Assistant}{January 2019 - June 2019}
\resumeItemListStart

\resumeItem{Teaching Assistant}{Instructed students in practical and
  theoretical machine learning methods, driven by Python and Tensorflow. Wrote
  supplementary course material and assisted with grading assignments.}
\resumeItem{Grader}{Provided constructive feedback and quantitative grades for
  Scientific Visualization and Intro to Comp.~Sci.~I \& II. Augmented classroom
  instruction via Piazza.}

\resumeItemListEnd


\resumeSubheading
{Epic Systems}{Madison, WI}
{Software Development Intern}{June 2018 - August 2018}
\resumeItemListStart

\resumeItem{Predictive Modeling}{Developed custom machine learning functionality
  to SlicerDicer, a web-based tool enabling clinicians to investigate health
  data.}

\resumeItemListEnd

\resumeSubheading
{IBM Research - Almaden}{San Jose, CA}
{Research Intern}{June 2017 - September 2017}
\resumeItemListStart

\resumeItem{Systolic Data Flow of CNNs}{Developed algorithms for systolic data
  flow of Convolutional Neural Networks with analog-memory-based deep
  learning. Simulated forward propagation time and estimated a speedup over
  state-of-the-art GPUs by two orders of magnitude.}

\resumeItemListEnd

% \resumeSubheading
% {University of Chicago}{Chicago, IL}
% {Research Assistant}{June 2016 - March 2017}
% \resumeItemListStart
% \resumeItem{Cosmic Rays}{Analyzed the Fermi LAT database for possible gamma
%   ray events from Jupiter's Great Red Spot. Concluded the GRS emits no
%   significant gamma rays above 20 MeV.}
% \resumeItemListEnd

\resumeSubHeadingListEnd

% --------PUBLICATIONS AND PATENTS------------

\section{Patents and Publications}
\resumeSubHeadingListStart
\item Hundt, Andrew, \textbf{Benjamin Killeen}, Heeyeon Kwon, Chris Paxton, and
  Gregory D. Hager. “‘Good Robot!’: Efficient Reinforcement Learning for
  Multi-Step Visual Tasks via Reward Shaping.” ArXiv:1909.11730 [Cs], September
  25, 2019. \url{http://arxiv.org/abs/1909.11730}.
\item Burr, Geoffrey and \textbf{Killeen, Benjamin}. Efficient Processing
  Convolutional Neural Network Layers using Analog-Memory-Based Hardware.
  Provisional U.S. Patent filed October 12, 2018.
\item Ambrogio, S., Narayanan, P., Tsai, H., Shelby,, R., Boybat, I., Nolfi,
  C.D., Sidler, S., Giordano, M., Bodini, M., Farinha, N., \textbf{Killeen,
    B.}, Cheng, C., Jaoudi, Y., and Burr, G.  ``Equivalent-Accuracy Accelerated
  Neural Network Training using Analog Memory.'' \textit{Nature} 558:60 - 67
  (2018). \url{https://rdcu.be/TTx2}
 \resumeSubHeadingListEnd

% --------SKILLS------------
\section{Skills}

Python \delim Tensorflow/Keras \delim PyTorch \delim C \delim Scala \delim Java
\delim MatLab \delim JavaScript \delim LaTeX \delim Haskell \delim Emacs

Communication Skills \delim Scientific Writing \delim Experimental Design
\delim Neural Networks

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

\resumeSubItem{Artifice}{High precision object detection in scientific images,
  driven by Deep Neural Networks, available at
  \href{https://github.com/benjamindkilleen/artifice}{github.com/benjamindkilleen/artifice}}.

\resumeSubItem{Creative Writing}{Science fiction novel detailing Martians'
  return to a long-abandoned Earth.}

\resumeSubHeadingListEnd

% -----------COURSEWORK-----------------
\section{Coursework}

Deep Learning \delim Computer Integrated Surgery \delim
Unsupervised Learning \delim Computer Vision \delim
Machine Learning

Operating Systems \delim Networks \delim Scientific Visualization
\delim Computer Systems \delim Programming Languages

Honors Combinatorics \delim Honors Algorithms \delim Honors Discrete Math
\delim Multivariate Calculus \delim Linear Algebra

Quantum Mechanics I \& II \delim Classical Mechanics \delim Electronics
\delim Electricity and Magnetism \delim Statistics

% \resumeSubItem{Physics}{Quantum Mechanics, Classical Mechanics, Electronics,
%   Electricity and Magnetism}
% \resumeSubItem{Mathematics}{Statistics, Honors Calculus (I, II, III)}

% --------INTERESTS------------
% \section{Interests}

% Creative Writing \delim Sailing \delim Running \delim Bouldering%  \delim Humans
% % vs Zombies
  
%-------------------------------------------
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
